\documentclass[letter,sans]{moderncv}
\usepackage[margin=0.8in]{geometry}
\moderncvtheme[blue]{classic}

\firstname{Diana}
\familyname{Arrieta}
\address{663 Ehrhorn Ave. \# 4\\Mountain View, CA 94041\\}
\phone{1-562-294-3399}
\email{darrieta.agent@gmail.com}

\begin{document}
\maketitle

\vspace{-0.6in}

\section{Employment History}

\cventry{01/2018--Present}{Site Reliability Engineer II}{Collective Health, Inc.}{San Francisco, CA}{}
{Deliver better running production applications to be quick, efficient, secure, distributed and fault-tolerant. Automating away operational effort and complexity, moderating blameless postmortems, and shifting from reactive responses to outages to proactive identification and mitigation of operational risks.\\
  \textbf{Projects}:
  \begin{itemize}
  \item Deployment of a HIPAA compliant AWS account to use with Databricks for use in Data Science and Analytics workflows.
  \item Configuring retention of SFTP data on EC2 and S3 with automatic sync to Box and daily cleanup.
  \item Created standards in production readiness by authoring an internal readiness manifesto and checklist.
  \end{itemize}
}

\cventry{01/2016--01/2018}{Senior IT Support Engineer}{Collective Health, Inc.}{San Francisco, CA}{}
{Responsible for the critical infrastructure and systems which keep the business up and running at all times. Understanding of workflows and needs across all of organizations is key to operational efficiency, and efficacy.\\
  \textbf{Projects}:
  \begin{itemize}
  \item Administration and automation of the G Suite domain which includes: onboarding, device policy, account auditing, subdomains, TLS, Chrome devices
  \item Administration of Okta and application deployment
  %\item User, group, client and partner management of permissions on SFTP servers
  \item Deployment of SSH Key Management to IT managed platforms with Ansible
  \item Rolled out SentinelOne to all JAMF macOS managed laptops
  %\item Setup a content management system for dashboards
  \end{itemize}
}

\cventry{08/2013--09/2015}{Corporate Operations Engineer and Internal Technology Resident}{Google, Inc.}{Mountain View, CA \& London, UK}{}
{Focusing on internal onsite support and primarily acting as a liaison between technical and non-technical groups, operations engineers seek to enhance Google's infrastructure and internal services. By developing skills in computer networking, software development, site reliability engineering and system administration, engineers are encouraged in making internal support infrastructure modular, efficient, and useful.\\
  \textbf{Projects}:
  \begin{itemize}
    \item Automated the booking of video conference rooms for a troubleshooting session when a support request is created for one, reducing the workload by 75\%.
    %\item Triaged desktop issues for a 6000 employee shuffle.
    %\item Made a custom configuration for specialized hardware for use in accessibility.
    %\item Documented the process of disabling and removing deskphones from conference rooms.
    %\item Finding and flagging support requests that have a cold handoff.
    \item Mentor new residents in common break and fix scenarios for Linux machines.
  \end{itemize}
  \textbf{Security Operations Engineer, Client Platform Hardening}:
  \begin{itemize}
    \item Using audit logs and SQL, found the most common use cases of root privileges which included package installation, configuration, and use of specialized software which required administrative rights to use.
    %\item Triage security requests for root privileges, whitelisting software binaries, whitelisting websites, and creating certificates for mobile development.
  \end{itemize}
  \textbf{Building Automation and Security Engineer}:
  \begin{itemize}
    %\item Maintaining and tracking issues with over 300 guest registration kiosks
    %\item Managing user roles and badge access of over 90,000 employees via the use of C-Cure 9000
    \item Provisioning hardware and network access for physical security infrastructure, including iStar and DVTel servers
  \end{itemize}
}

%\cventry{06/2009--03/2013}{Student Assistant - Tier 2}{I\&IT Support}{Pomona, CA}{}{Technical support for faculty and staff around campus ranging from installation, updating and troubleshooting software and hardware, imaging and managing computers from various departments, and ensuring destruction of sensitive data from surveyed computers. Writing small scripts to automate the installation of software or for running repetitive tasks.}

%\cventry{09/2007--06/2009}{Student Assistant - Tier 1}{I\&IT Support}{Pomona, CA}{}
%{Technical support for the campus students, faculty, and staff with various campus services and configuring e-mail, wireless, and FTP clients. Basic troubleshooting of wireless access issues.}
%\vspace{.5em}
% \cventry{07/2006--09/2006}{Cashier - In-Restaurant}{Burger King}{South Gate, CA}{}
% {Take customer orders accurately and efficiently.\\
% Maintain workplace organization and cleanliness}

\section{Technical Details}
\cvline{Languages}{
BASH, HTML, CSS, Javascript, \LaTeX{}, Python, SQL}
\cvline{Experience}{
IT (12 years), Windows Administration (7 years), Linux Administration (4 years)}
\cvline{Software}{Git, Vagrant, Docker, Terraform, Kubernetes, Amazon EMR, Spark, Jupyter}
\cvline{Certifications}{LPIC-1, SUSE CLA, Comptia Linux+}

%cvline{Old Stuff}{Git, Vagrant, Avigilon, JAMF, Okta, JIRA, G Suite, Serv-U SFTP, REST APIs, Android (3 years), Mac OSX Administration (3 years), Google Apps Script}

\section{Education}
\cventry{2009--2013}{MS, Computer Science}{California State Polytechnic University}{Pomona, CA}{}{}
%\cvline{GPA:}{\small 3.37}
\cventry{2005--2009}{BS, Computer Science}{California State Polytechnic University}{Pomona, CA}{}{}
%\cvline{GPA:}{\small 3.20}

%\section{Volunteer Work}
%\begin{itemize}
%\item{Organizing and leading the Women in Tech group at Collective Health}
%\end{itemize}

%\section{Related Coursework}
%\cvline{Undergraduate}{
%Computer Networks,
%Database Systems,
%Object Oriented Design \& Programming,
%Operating Systems,
%Secure Communication,
%Symbolic Programming,
%Unix and Scripting,
%Web Design and Programming
%}

%\cvline{Graduate}{
%Advanced Algorithm Design \& Analysis,
%Advanced Software Engineering,
%Computer Image Processing,
%Cyber Security,
%Multimedia Systems,
%Natural Language Processing
%}
%\section{Existing Work}
%\subsection{The Amazing Bear Hunt}
%\cvline{}{http://abh.berkeley.edu/}
%\subsection{CS299 Final Project}
%\cvline{}{http://www.csupomona.edu/\textasciitilde darrieta/}
\end{document}
